Efficient pedigree recording for fast population genetics simulation

### 2017-12-30 forwards_paper.tex
Note missing cites

\begin{figure}
    \begin{center}
        \includegraphics{simplify-state-diagram}
    \end{center}
    \caption{
        A depiction of the state of the simplification algorithm
        at each point in time,
        in the example of Figure~\ref{fig:method_diagram}A.
        As in that figure, blue numbers denote the crossing over location in a meiosis --
        for instance, $G$ and $H$ were parents to $I$,
        who inherited the left 70\% of the chromosome from $G$ and the remainder from $H$.
        \label{fig:simplify_state}
    }
\end{figure}

>>>>

\begin{figure}
    \begin{center}
        \includegraphics{simplify-state-diagram}
    \end{center}
    \caption{
        A depiction of the state of the simplification algorithm
        at each point in time,
        in the example of Figure~\ref{fig:method_diagram}.
        \label{fig:simplify_state}
    }
\end{figure}
